Poster Data Analysis

### 2018-09-12 notebooks/poster_analysis.Rmd
last adjustment to dendrogram

# Arrange both plots into one figure
grid.arrange(arrangeGrob(p1 + theme(plot.margin=margin(50,-2,135,0)),
                         heights = c(1.9,-0.097)),
             arrangeGrob(p2 + theme(axis.text.y=element_blank(),
                                    plot.margin = margin(0,0,0,-8)),
                         heights=c(0.98,-0.03)), 
             ncol=2)

>>>>

# Arrange both plots into one figure
grid.arrange(arrangeGrob(p1 + theme(plot.margin=margin(51,-2,135,0)),
                         heights = c(1.9,-0.097)),
             arrangeGrob(p2 + theme(axis.text.y=element_blank(),
                                    plot.margin = margin(0,0,0,-8)),
                         heights=c(0.98,-0.03)), 
             ncol=2)
